Bullet Data Preparation for LIME Diagnostics Paper

### 2020-09-21 code/02-data-preparation.Rmd
updated figure

```{r}
rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2]
new_pred = predict(bulletxtrctr::rtrees, bullet_train_filtered %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
```

@@

>>>>

```{r}
rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2]
new_pred = predict(bulletxtrctr::rtrees, bullet_train_filtered %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
new_pred_full = predict(bulletxtrctr::rtrees, bullet_train_raw %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
```

@@

Plot showing distributions of predictions from `rtrees` and new predictions made on full training data:

```{r}
data.frame(data = c(rep("rtrees", length(rtrees_pred)), rep("new predictions on full data", length(new_pred_full))), pred = c(rtrees_pred, new_pred_full)) %>%
  ggplot(aes(x = pred, fill = data)) + 
  geom_density(alpha = 0.75)
```

```{r}
data.frame(rtrees_pred = sort(rtrees_pred), new_pred = sort(new_pred))
```
